\LARGE \bf TODO Name this thing

### 2012-02-17 papers/itsc_2012/root.tex
finished abstract and first 2 paragraphs of introduction

\begin{abstract}
Autonomous vehicle technology have seen great advancements in recent years and are closer to being commercially viable. Driverless cars provide opportunities for optimizing traffic across cities in ways not possible before. This paper explores such scenarios and introduces a new traffic micro-simulator named AORTA. AORTA emphasizes research using scale simulations generated from OpenStreetMap data. This paper presents parsing map through the simulator and using the AORTA simulator. It concludes with some preliminary results that demonstrate the power of this simulator.   
\end{abstract}

@@

Autonomous vehicles have seen tremendous progress in recent years. The DARPA Challenge in 2004 saw the farthese distance being traversed autonomously as In 2004, no autonomous vehicle was able to complete the course set out in the first DARPA Challenge. By 2007, 5 vehicles finished the course of 130 miles in urban environments. By 2011, autonomous vehicles projects have now touched 160,000 miles and an autonomous car drove for 13,000 miles in Europe. Autonomous cars are here to stay, and this changes how traffic is dealt with in the forseeable future. The infrastructure will change to support autonomous vehicles, but it is hard to say more about our traffic demands. Will we be able to gain more roads in the future. Do we have the space to expand and will autonomous vehicles be able to reach your doorstep.

@@

To use road data, we can use OpenStreetMap. xml files exported using OSM are directly read by a tool and parsed to create an understandable map. Our simulator then uses this map to create the simulation and can introduce an army of agents to simulate traffic inside the simulator.

@@

\begin{thebibliography}{99}

\bibitem{c1} G. O. Young, ÒSynthetic structure of industrial plastics (Book style with paper title and editor),Ó 	in Plastics, 2nd ed. vol. 3, J. Peters, Ed.  New York: McGraw-Hill, 1964, pp. 15Ð64.
\end{thebibliography}

>>>>

\begin{abstract}
Autonomous vehicles have seen great advancements in recent years and such vehicles are now ever closer to being commercially available. The advent of driverless cars provides opportunities for optimizing traffic in ways not possible before. This paper introduces an open source multi-agent traffic simulator called AORTA, which stands for \textit{Approximately Orchestrated Road Network Automata}, and demonstrates its usage for optimizing autonomous traffic at a city-wide scale. AORTA creates scale simulations by generating maps using publicly available road data from \textit{OpenStreetMaps} (OSM). Simulations can be set up in the few minutes it takes to export data for the region of interest from OSM. AORTA focuses on interactions between agents by defining \textit{behaviors} for individual vehicles and intersections. These behaviors allow agents to interact with each other as well as with an external \textit{overseer} that is responsible for optimizing traffic flow. Overseers can interact with these agents to allow for dynamic route re-planning to reduce traffic load, optimized intersection navigation, and improved car following. \commentpk{rest devoted to application}
\end{abstract}

@@

Autonomous vehicle technology has made tremendous progress in the last decade. In 2004, the farthest distance travelled by a vehicle autonomously in the the DARPA Grand Challenge of 2004 was $11.9km$ \cite{cnnGrandChallenge2004}. By 2007, six of the competing teams completed the $96km$ course set for the DARPA Urban Challenge \cite{spectrumUrbanChallenge2007}. They did so while following the same traffic laws followed by human drivers, navigating around moving vehicles and following correct intersection precedence order. Since then, Google's driverless cars have clocked more than $250,000km$ on public roads in urban California, USA \cite{tedThrun2011}. In 2010, researchers from the University of Parma successfully completed an autonomous \textit{intercontinental} run from Parma, Italy to Shanghai, China \cite{cnnVislab2010}. The successful completion of all these milestones indicates that autonomous cars are here to stay, and are ever closer to becoming commercially available.

The arrival of driverless cars presents a number of challenges that need to addressed in the near term. Road infrastructure needs to be updated to better support autonomous vehicles. A number of laws and safety concerns need to be addressed in the context of driverless cars. Human drivers need new methodologies to interact with autonomous drivers on public roads. At the same time, driverless cars provide opportunities of solving traffic problems in ways that were never before possible. For instance, autonomous cars can be quickly diverted to make way for emergency vehicles responding to an accident. Even day-to-day traffic issues such as congestion could potentially be greatly reduced by effective management of traffic flow. This paper attempts to address some of these problems.

The infrastructure will change to support autonomous vehicles, but it is hard to say more about our traffic demands. Will we be able to gain more roads in the future. Do we have the space to expand and will autonomous vehicles be able to reach your doorstep.

@@

To use road data, we can use OpenStreetMap. xml files exported using OSM are directly read by a tool and parsed to create an understandable map. Our simulator then uses this map to create the simulation and can introduce an army of agents to simulate traffic inside the simulator. Real road data is necessary for such simulations due to ever limited space inside cities, which makes it so that in the near future all the infrastructure will become friendly towards autonomous vehicles. But we will still continue to use the same roads.

@@

\bibliographystyle{IEEEtran}
\bibliography{root}
